Figures

### 2022-02-07 Figures.Rmd
07 Jan return

plots_paper$pupil_course<- tmp.df4_full_stim_downs_jun2021_60bins_no_na %>%
  subset(is.na(mediansplit_sample_arousal2) == FALSE)%>%
  subset(Group == "NT")%>%
  subset(pp_arousal_outler == FALSE)%>%
  subset(pupil_outlier == FALSE)%>%

  ggplot(aes(x = timerezero3, y = pup_basCor, color = Arpisal_newlab, linetype = mediansplit_sample_valence2)) +
  # aes(group = ssid),
  geom_smooth()+
  # stat_smooth(size=1.5, method = "loess", level = 0.95, 
  #   fullrange = TRUE) + 
  # stat_smooth(aes(group=mediansplit_ground_arousal, color = mediansplit_ground_arousal), size = 3)+  
# theme_classic()+
  ylab("Pupil size (z)")+
  xlab("Time (s)")+
  p$graphstyle+
   # scale_color_brewer(palette = "Dark2")+
  xlim(0,6)+
   labs(color  = "Subjective valence", linetype = "Subjective arousal")

plots_paper$pupil_course<- plots_paper$pupil_course+
    guides(color=guide_legend(nrow=2, byrow=TRUE))

@@

  xlab("Subjective valence (z)")+
  ylab(expression(Delta*" heart rate (bpm)"))+
    # p$graphstyle+ylim(-4,1)+
  ggpubr::stat_cor(label.y = -1)

@@

unique(tmp.df4_full_stim_downs_jun2021_60bins_no_na1$ssid)
plots_paper$arousal_clust<- clustering_new %>%
  subset(!is.na(Cluster))%>%
  # subset(ssid_num>303)%>%^
  group_by(ssid, Cluster)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  # mutate(arousal2 = abs(arousal))%>%
  subset(arousal> -9)%>%
  ggboxplot(x = "Cluster", y = "arousal",
          color = "Cluster")+
  geom_jitter(width = .1, alpha = .2)+
    stat_summary(aes(group =ssid), geom =  'line', alpha = .2, size = .1)+
  xlab("Cluster")+
  ylab("Subjective arousal \n (calm - agitated)")+
  p$graphstyle+ theme(legend.position = "none")
  # stat_compare_means(comparisons = my_comparisons)+ # Add pairwise comparisons p-value
  # stat_compare_means(label.y = 9)
plots_paper$arousal_clust
# valence cluster

@@

ggsave("gaze_control.tiff",gaze_control, device = "tiff", width = 13, height = 6, dpi = 800)
https://www.r-bloggers.com/2017/09/multi-dimensional-reduction-and-visualisation-with-t-sne/
  https://cran.r-project.org/web/packages/Rtsne/Rtsne.pdf
https://uc-r.github.io/kmeans_clustering
```

>>>>

tmp.df4_full_stim_downs_jun2021_60bins_no_na$newlab<- paste0(tmp.df4_full_stim_downs_jun2021_60bins_no_na$Arpisal_newlab, paste0(tmp.df4_full_stim_downs_jun2021_60bins_no_na$mediansplit_sample_valence2))

unique(tmp.df4_full_stim_downs_jun2021_60bins_no_na$newlab)
plots_paper$pupil_course<- tmp.df4_full_stim_downs_jun2021_60bins_no_na %>%
  subset(is.na(mediansplit_sample_arousal2) == FALSE)%>%
  subset(Group == "NT")%>%
  subset(pp_arousal_outler == FALSE)%>%
  subset(pupil_outlier == FALSE)%>%

  ggplot(aes(x = timerezero3, y = pup_basCor, color = newlab, linetype = newlab)) +
  # aes(group = ssid),
  geom_smooth()+
  # stat_smooth(size=1.5, method = "loess", level = 0.95, 
  #   fullrange = TRUE) + 
  # stat_smooth(aes(group=mediansplit_ground_arousal, color = mediansplit_ground_arousal), size = 3)+  
# theme_classic()+
  ylab("Pupil size (z)")+
  xlab("Time (s)")+
  p$graphstyle+
   scale_color_brewer(palette = "Dark2")+
  xlim(0,6)+
   labs(color  = "Subjective valence", linetype = "Subjective arousal")

# newlab
plots_paper$pupil_course<- plots_paper$pupil_course+
    guides(color=guide_legend(nrow=2, byrow=TRUE))

@@

  xlab("Subjective valence (z)")+
  ylab(expression(Delta*" heart rate (bpm)"))+
    p$graphstyle
  # ggpubr::stat_cor(label.y = -1)

@@

library(ggpubr)
unique(tmp.df4_full_stim_downs_jun2021_60bins_no_na1$ssid)
plots_paper$arousal_clust<- clustering_new %>%
  subset(!is.na(Cluster))%>%
  # subset(ssid_num>303)%>%^
  group_by(ssid, Cluster)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  # mutate(arousal2 = abs(arousal))%>%
  subset(arousal> -9)%>%
  ggboxplot(x = "Cluster", y = "arousal",
          color = "Cluster")+
  geom_jitter(width = .1, alpha = .2)+
    stat_summary(aes(group =ssid), geom =  'line', alpha = .2, size = .1)+
  xlab("Cluster")+
  ylab("Subjective arousal \n (calm - agitated)")+
  p$graphstyle+ theme(legend.position = "none")+
  scale_y_continuous(breaks = c(-6, -4, 0, 4))
  # stat_compare_means(comparisons = my_comparisons)+ # Add pairwise comparisons p-value
  # stat_compare_means(label.y = 9)
plots_paper$arousal_clust
# valence cluster

@@

ggsave("gaze_control.tiff",gaze_control, device = "tiff", width = 13, height = 6, dpi = 800)
https://www.r-bloggers.com/2017/09/multi-dimensional-reduction-and-visualisation-with-t-sne/
  https://cran.r-project.org/web/packages/Rtsne/Rtsne.pdf
https://uc-r.github.io/kmeans_clustering
https://sciwheel.com/work/item/5365248/resources/12059185/pdf
```
